\documentclass[11pt, A4paper, english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage[colorlinks]{hyperref}
\usepackage{color}
\usepackage{tabularx}

\author{Torstein Solheim Ølberg}
\title{Diglossa}


\begin{document}
	\maketitle
	
	\section*{Description}
You are an employee at the company Diglossa, a company which works to spread the knowledge of languages across all panes of existence. Your job is to visit customers of the firm and "remind" them to keep up with their daily lessons. You occasionally receive names and locations of people who need a reminder and must pay them a visit as soon as possible. \\
As payment for your work, you are given an understanding of the language of magic to help you in your work as well as your own life. You are also given the lessons available from you company for free and expected to perform the tasks you are given or be treated the same way your customers would.

	\section*{The Actual Patron}
Your actual patron is the owl entity Di, who uses Diglossa to push his goal of spreading knowledge of languages to all creatures, no matter the cost. Di is an old entity with unknown origin and powers based around languages. It's knowledge of languages is unending, including the universal languages used to draw out magic from the fabric of the universe. Any customers of his front cover firm will be bound to a lifelong customership or suffer the consequences of being visited by one of the employees of Diglossa.

	\section*{Expanded Spell List}
You are given an extended spell list as well as the normal list for a warlock. These count as warlock spells for you. \\
		\begin{tabular}{|l|l|}
\hline
Spell Level & Spell Name \\
\hline
1st & Dissonant Whispers, Healing Word, Speak With Animals \\
2nd & Magic Mouth, Skywrite \\
3rd & Glyph of Warding, Mass Healing Word \\
4th & Compulsion \\
5th & Commune, Wrath of Nature \\
\hline
		\end{tabular}

	\section*{Book of Glossa}
You, like all of the customers of Diglossa, are given the book of Glossa. This is an empty magical book used to perform your daily tasks and lessons and this is where you get information on what tasks you have to perform each day. Each day, words will appear in the book and you have to answer questions either by writing the answer or speaking out loud to the book. This takes approximately one hour a day, and if you do not perform these tasks, you will be visited by a colleague who will "remind you of your lessons". If you lose your book you can wait until the next night and a colleague will visit you and give you a new book.

	\section*{Multilingual Work}
Since you are given a job where you need to be able to communicate with lots of different people, you are given powers to aid you. Twice per day, you can cast Comprehend Language without using a spell slot and this spell doesn't count as one of your spells known.

	\section*{Language Student}
You study languages with the help of Diglossa, and will learn additional languages throughout your life. You learn one new language every other level starting from 2nd level. You have to state what language you will learn next time, each time you learn a new one and also on level one. \\
Here is a list of possible language you could learn or you could ask your DM which would be available in your world. \\
		\begin{tabular}{l}
\textbf{Languages}
		\end{tabular} \\
		\begin{tabular}{l|l}
\hline
Abyssal & Kraul \\
Aarakocra & Loxodon \\
Celestial & Merfolk \\
Common & Minotaur \\
Deep Speech & Orc \\
Draconic & Primordial \\
Druidic & \indent Aquan \\
Dwarvish & \indent Auran \\
Elvish & \indent Ignan \\
Giant & \indent Terran \\
Gith & Sphinx \\
Gnomish & Sylvan \\
Goblin & Thieves' Cant \\
Gnoll & Undercommon\\
Halfling & Vedalkin \\
Infernal & \\
		\end{tabular}

	\section*{Pact of Diglossa}
At 3rd level, your company bestows you a limited knowledge of the languages of magic. When you gain this power you can inscribe one 1st level spell from any class into your book of Glossa. The spell you choose is a spell you can always inscribe into your book. This spell doesn't count as one of your spells known, and count as a warlock spell for you. Any time you find a new spell which you have the spell slots to cast, you can choose to switch out the spell you have inscribed with the one you have found, if you have the time and resources to do so. The cost of inscription is 50 gp, and 2 hours, per level of the spell. If you lose your book you start with your original 1st level spell again. \\
This also gives you the possibility to choose any of the eldritch invocations with the pact of tome prerequisite.

	\section*{Torpedo}
At 6th level your work for the company has given you experience of investigation, persuasion and intimidation. You gain proficiency in these skills. If you already have one of these three skills, you gain another of your choice.
	
	\section*{Multilingual Mind}
At 10th level you naturally commune and think in multiple languages at once, making your mind harder to penetrate and attacks less effective. You gain resistance to psychic damage and proficiency with intelligence saving throws. If someone tries to read your mind, they must perform an intelligence check, where the DC is 10 + the number of languages you know that they don't, to determine if they can understand your thoughts or not.

	\section*{Linguist}
At 14th level, your understanding of languages is so great you can combine different languages to understand sentences not based on any normal language. You can now use comprehend language to decode secret messages, both spoken and written, or arcane glyphs as well.

	\section*{Di's Word}
Starting at level 14 you have been promoted to a higher position. As a result of this, you are given the power to speak a word in the omnilingual language of Di even if the meaning of your word is beyond your mind. Once per long rest, as an action you can choose a target, speak a word an roll a d100. The result is determined by consulting the following table. \\
		\begin{tabular}{ll}
$01 - 10 =$ & Vicious Mockery \\
$11 - 55 =$ & Power Word Pain \\
$56 - 90 =$ & Power Word Stun \\
$91 - 95 =$ & Power Word Heal \\
$96 - 00 =$ & Power Word Kill
		\end{tabular}

\end{document}