\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{babel}
\usepackage{cite}
\usepackage{color}
\usepackage{enumitem}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{paralist}
\usepackage{pifont}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{wasysym}

\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\ding{51}}}}
\newcommand{\available}{$\square$}
\newcommand{\tabitem}{~~\llap{--}~~}
\newcommand{\tabtabitem}{~~~~~~\llap{$\bullet$}~~}
\newcommand{\tabtabtabitem}{~~~~~~~~~\llap{$\star$}~~}

\definecolor{url}{rgb}{0.1, 0.1, 0.4}

\graphicspath{{<Folderpath>}}
\hypersetup{colorlinks, urlcolor = url}

\textwidth = 550pt
\oddsidemargin = 0pt
\hoffset = -40pt

\addtolength{\voffset}{-3cm}

\begin{document}
	\begin{center}
\Huge \textbf{Günter Shnabelcknese}
	\end{center}
	\begin{multicols}{2}
\noindent \begin{tabularx}{95mm}{@{}l l}
\Large \textbf{Personality:} 	& 						\\
\hline
\textbf{Race:} 					& Orc		 			\\
\textbf{Sex:} 					& Male	 				\\
\textbf{Class:}					& Barbarian				\\
\textbf{Level:} 				& 6						\\
\textbf{Age:} 					& 16 years old			\\
\textbf{Height:} 				& 190 meters tall 		\\
\textbf{Muscle Mass:} 			& Medium 				\\
\textbf{Colour:} 				& Maroon skin tone	 	\\
\textbf{Mass:} 					& 113 kg		 		\\
\textbf{Nature:} 				& Chaotic Evil
		\end{tabularx} \\
\textbf{Backstory:} \\
I was born in Nerezdrul where I belonged to an orc coast tribe called The Hisenschnaiser. At one point a neighboring tribe raided our village and humiliated us. As a result of this, half of all our warriors where sent out to train and become stronger. I am one of them, and has been roaming the lands ever since. I wish to one day reach ultimate strength, and I will return to fight and take back our honor.

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l}
{\Large \textbf{Languages:}} \\
\hline
\tabitem Common \\
\tabitem Orc \\
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l l}
\Large \textbf{Stats:}		 	& 									\\
\hline
\textbf{Hit points:} 			& 65/65  							\\
\textbf{Hit dice available:}	& 6/6								\\
\textbf{Armour class:} 			& 15							 	\\
\textbf{Initiative:} 			& +2								\\
\textbf{Speed:} 				& 40	 							\\
\textbf{Passive Wisdom:} 		& 11			 					\\
\textbf{Proficiency bonus:}		& +3								\\
\textbf{Exp:} 					& 14000/23000
		\end{tabularx}

\vspace{2mm}

\noindent \begin{tabularx}{95mm}{@{}l}
{\Large \textbf{Skill Proficiencies:}} \\
\hline
\tabitem Athletics \\
\tabitem Intimidation \\
\tabitem Survival
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l|c|c}
\multicolumn{3}{@{}l}{\Large \textbf{Attributes:}} \\
\hline
		\end{tabularx}
\noindent \begin{tabular}{@{}l|c|c}
\textbf{Category:} 			& \textbf{Value:} 	& \textbf{Mod:} \\
\hline
Strength 					& 19 				& +4		\\
Dexterity 					& 14 				& +2		\\
Wisdom 						& 13				& +1		\\
Constitution 				& 16 				& +3		\\
Intelligence 				& 9 				& -1		\\
Charisma 					& 11 				& 0
		\end{tabular}

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l}
{\Large \textbf{Save Throws:}} \\
\hline
\tabitem Strength \\
\tabitem Constitution
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l}
{\Large \textbf{Weapons:}} \\
\hline
\tabitem Eruption (proficient) (Attuned) 1d12 + 4 damage \\
\tabtabitem This greataxe emits light in a 30 foot radius when held. \\
\tabtabitem Deals an additional 2d6 fire damage. \\
\tabtabitem On a natural 1 the wielder also takes damage. \\
\tabitem Greataxe (proficient) 1d12 + 4 damage \\
\tabitem Handaxe (proficient) 1d6 + 4 damage \\
\tabitem Javelin (proficient) 1d6 + 4 damage
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l}
{\Large \textbf{Chosen Abilities and Traits:}} \\
\hline
\tabitem Rage \\
\tabtabitem Primal Path - Path of the Storm Herald \\
\tabtabtabitem Storm Aura - Sea \\
\tabitem Unarmoured Defence \\
\tabitem Reckless Attack \\
\tabitem Danger Sense \\
\tabitem Extra Attack \\
\tabitem Fast Movement \\
\tabitem Storm Soul - Sea
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{95mm}{@{}l}
{\Large \textbf{Rage:}} \\
\hline
\available \available \available \available
		\end{tabularx}
	\end{multicols}

\clearpage

	\begin{center}
{\LARGE \textbf{Items}}
	\end{center}

	\begin{tabularx}{\textwidth}{X|r}
Item & Weight [kg] \\
\hline
Backpack									&			\\
Bedroll										&			\\
Greataxe									&			\\
2x Handaxe									&			\\
Javelin										&			\\
Mess kit									&			\\
10x Rations									&			\\
15m Rope									&			\\
Tinderbox									&			\\
10x Torch									&			\\
Waterskin									&			\\
Eruption									&			\\
2 sp					 					& 			\\
\hline
Sum 										&
	\end{tabularx}

\vspace{10mm}

\textbf{Carrying capacity:} \\

	\begin{tabular}{l|c}
Category & Weight [kg] \\
\hline
Lightly encumbered 	& 0 - 47.5 	\\
Encumbered 			& 47.5 - 95 \\
Heavily encumbered	& 95 - 142.5
	\end{tabular}
\end{document}