\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{babel}
\usepackage{cite}
\usepackage{color}
\usepackage{enumitem}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{paralist}
\usepackage{pifont}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{wasysym}

\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\ding{51}}}}
\newcommand{\available}{$\square$}
\newcommand{\tabitem}{~~\llap{--}~~}
\newcommand{\tabtabitem}{~~~~~~\llap{$\bullet$}~~}

\definecolor{url}{rgb}{0.1, 0.1, 0.4}

\graphicspath{{<Folderpath>}}
\hypersetup{colorlinks, urlcolor = url}

\textwidth = 550pt
\oddsidemargin = 0pt
\hoffset = -40pt

\addtolength{\voffset}{-3cm}

\begin{document}
	\begin{center}
\Huge \textbf{Odegar Penelope}
	\end{center}
	\begin{multicols}{2}
\noindent \begin{tabularx}{\linewidth}{@{}l l}
\Large \textbf{Personality:} 	& 						\\
\hline
\textbf{Race:} 					& Dragonborn 			\\
\textbf{Sex:} 					& Female 				\\
\textbf{Class:}					& Ranger				\\
\textbf{Level:} 				& 5						\\
\textbf{Age:} 					& 15 years old			\\
\textbf{Height:} 				& 2 meters tall 		\\
\textbf{Muscle Mass:} 			& Medium 				\\
\textbf{Colour:} 				& Green skin tone	 	\\
\textbf{Mass:} 					& 110 kg		 		\\
\textbf{Nature:} 				& LG
		\end{tabularx} \\
\textbf{Backstory:} \\
Belonging to the Odegar wood tribe, Penelope once went out into the woods to hunt and train. Her drive is to one time take down a Tyrannosaurus Rex by herself. These last 2 years she has roamed the woods, caring for herself and getting to know the creatures of the wild, but she has forgotten where her tribe lives and has not really had anything to do with people for the last 2 years. She is kind of childish and very inexperienced with people. She also don't know much about the standard customs of society.

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Languages:}} \\
\hline
\tabitem Common \\
\tabitem Draconic \\
\tabitem Sylvan
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l l}
\Large \textbf{Stats:}		 	& 									\\
\hline
\textbf{Hit points:} 			& 44/44					 			\\
\textbf{Hit dice available:}	& 5/5d10							\\
\textbf{Armour class:} 			& 11 $+$ 5 $=$ 16				 	\\
\textbf{Initiative:} 			& +5								\\
\textbf{Speed:} 				& 30		 						\\
\textbf{Passive Wisdom:} 		& 10 $+$ 3 $=$ 13 					\\
\textbf{Proficiency bonus:}		& +3								\\
\textbf{Exp:} 					& 6500/14000
		\end{tabularx}

\vspace{2mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Skill Proficiencies:}} \\
\hline
\tabitem Nature \\
\tabitem Stealth \\
\tabitem Perception \\
\tabitem Athletics \\
\tabitem Survival
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l|c|c}
\multicolumn{3}{@{}l}{\Large \textbf{Attributes:}} \\
\hline
		\end{tabularx}
\noindent \begin{tabular}{@{}l|c|c}
\textbf{Category:} 			& \textbf{Value:} 	& \textbf{Mod:} \\
\hline
Strength 					& 9 + 2 = 11		& 0			\\
Dexterity 					& 18 + 2 = 20		& +5		\\
Wisdom 						& 17				& +3		\\
Constitution 				& 14 				& +2		\\
Intelligence 				& 9 				& -1		\\
Charisma 					& 13 + 1 = 14		& +2
		\end{tabular}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Save Throws:}} \\
\hline
\tabitem Strength \\
\tabitem Dexterity \\
		\end{tabularx}
\noindent Spell save DC $= 8 + 3 + 3 = 14$

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Weapons:}} \\
\hline
\tabitem Shortsword (proficient) 1d6 piercing damage \\
\tabitem Longbow (proficient) 1d8 piercing damage \\
\tabitem Staff (proficient) 1d6 bludgeoning damage
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Choosen Abilities and Traits:}} \\
\hline
\tabitem Draconic Ancestry \\
\tabtabitem Green(Poison, 15 feet cone, Con. save) \\
\tabitem Breath Weapon \\
\tabtabitem 1/short rest. \\
\tabtabitem 2d6 damage (DC $= 8 + 2 + 3 = 13$) \\
\tabitem Damage Resistance \\
\tabitem Outlander \\
\tabtabitem Wanderer \\
\tabitem Favoured Enemy (Beasts) \\
\tabtabitem Advantage on tracking and infos checks \\
\tabitem Natural Explorer (Forests) \\
\tabtabitem Int. and Wis. checks have prof. bonus doubled \\
\tabtabitem Not slowed down by terrain \\
\tabtabitem Never naturally lost \\
\tabtabitem Always alert \\
\tabtabitem Move stealthily if alone \\
\tabtabitem Find twice as much food \\
\tabtabitem Learn exact number and time since passed when \\
tracking \\
\tabitem Fighting style (Archery) \\
\tabtabitem Attack roll +2 \\
\tabitem Ranger Archetype (Hunter) \\
\tabtabitem Colossus Slayer (1d8 extra if creature is damaged) \\
\tabitem Primeval Awareness \\
\tabitem Extra Attack
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l c}
{\Large \textbf{Spell Slots:}} \\
\hline
1st level slot & \available \\
1st level slot & \available \\
1st level slot & \available \\
1st level slot & \available \\
2nd level slot & \available \\
2nd level slot & \available
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Item Proficiencies:}} \\
\hline
\tabitem Flute \\
\tabitem Light Armour \\
\tabitem Medium Armour \\
\tabitem Shields \\
\tabitem Simple Weapons \\
\tabitem Martial Weapons
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Spell list}} 		\\
\hline
\textbf{1st. Level Spells:}			\\
Goodberry							\\		
Hail of Thorns (bonus action)		\\
Hunters Mark (bonus action)			\\

\textbf{2nd. Level Spells:}			\\
Spike Growth
		\end{tabularx}
	\end{multicols}

\clearpage

	\begin{center}
{\LARGE \textbf{Items}}
	\end{center}

	\begin{tabularx}{\textwidth}{X|r}
Item & Weight [kg] \\
\hline
5?10 gp					 					& 			\\
Staff	 		 							& 			\\
Hunting Trap	 		 					& 			\\
Sabretooth 		 							& 			\\
Traveller's Clothes	 						& 			\\
A pouch	 		 							& 			\\
Leather Armour	 							& 			\\
2 Shortswords	 							& 			\\
Backpack		 							& 			\\
Bedroll			 							& 			\\
Mess kit		 							& 			\\
Tinderbox		 							& 			\\
10 x Torch	 								& 			\\
10 x Ration		 							& 			\\
Waterskin		 							& 			\\
50 feet of hempen rope						& 			\\
Longbow			 							& 			\\
20 x Arrow		 							& 			\\
\hline
Sum 										& 
	\end{tabularx}

\vspace{10mm}

\textbf{Carrying capacity:} \\

	\begin{tabular}{l|c}
Category & Weight [kg] \\
\hline
Lightly encumbered 	& 0 - 27.5 	\\
Encumbered 			& 27.5 - 55 \\
Heavily encumbered	& 55 - 82.5
	\end{tabular}
\end{document}