\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{babel}
\usepackage{cite}
\usepackage{color}
\usepackage{enumitem}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{paralist}
\usepackage{pifont}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{wasysym}

\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\ding{51}}}}
\newcommand{\available}{$\square$}
\newcommand{\tabitem}{~~\llap{--}~~}
\newcommand{\tabtabitem}{~~~~~~\llap{$\bullet$}~~}

\definecolor{url}{rgb}{0.1, 0.1, 0.4}

\graphicspath{{<Folderpath>}}
\hypersetup{colorlinks, urlcolor = url}

\textwidth = 550pt
\oddsidemargin = 0pt
\hoffset = -40pt

\addtolength{\voffset}{-3cm}

\begin{document}
	\begin{center}
\Huge \textbf{Vidarrrh Burheim}
	\end{center}
	\begin{multicols}{2}
\noindent \begin{tabularx}{\linewidth}{@{}l l}
\Large \textbf{Personality:} 	& 						\\
\hline
\textbf{Race:} 					& Human	 				\\
\textbf{Sex:} 					& Male 					\\
\textbf{Class:}					& Rogue and Artificer	\\
\textbf{Level:} 				& 6: 3 R, 3 A			\\
\textbf{Age:} 					& 67 years old			\\
\textbf{Height:} 				& 1.73 meters tall 		\\
\textbf{Muscle Mass:} 			& Medium 				\\
\textbf{Colour:} 				& Pink skin tone	 	\\
\textbf{Mass:} 					& 88 kg			 		\\
\textbf{Nature:} 				& Chaotic Neutral
		\end{tabularx} \\
\textbf{Backstory:} \\
Born into a family of pirates, he learned the ways of the other side of the law. However, he was more interested in the making of different bombs and ventured out to learn the art of the chemist. This lead him to teaching and he is now a retired chemist teacher seeking adventure in his old days.

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Languages:}} \\
\hline
\tabitem Common \\
\tabitem Thieves' Cant \\
\tabitem Orc
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l l}
\Large \textbf{Stats:}		 	& 									\\
\hline
\textbf{Hit points:} 			& 45/45 							\\
\textbf{Hit dice available:}	& 6/6 d8 							\\
\textbf{Armour class:} 			& 16							 	\\
\textbf{Initiative:} 			& +4								\\
\textbf{Speed:} 				& 30		 						\\
\textbf{Passive Wisdom:} 		& 12	 							\\
\textbf{Proficiency bonus:}		& 3									\\
\textbf{Spells Prepared:} 		& 5									\\
\textbf{Exp:} 					& 6500/14000
		\end{tabularx}

\vspace{2mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Skill Proficiencies:}} \\
\hline
\tabitem Intimidation \\
\tabitem Medicine \\
\tabitem Deception \\
\tabitem Performance \\
\tabitem Athletics \\
\tabitem Perception
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l|c|c}
\multicolumn{3}{@{}l}{\Large \textbf{Attributes:}} \\
\hline
		\end{tabularx}
\noindent \begin{tabular}{@{}l|c|c}
\textbf{Category:} 			& \textbf{Value:} 	& \textbf{Mod:} \\
\hline
Strength 					& 11 + 1 = 12		& +1		\\
Dexterity 					& 18 + 1 = 19 		& +4		\\
Wisdom 						& 12 + 1 = 13		& +1		\\
Constitution 				& 14 + 1 = 15 		& +2		\\
Intelligence 				& 18 + 1 = 19 		& +4		\\
Charisma 					& 14 + 1 = 15		& +2
		\end{tabular}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Save Throws:}} \\
\hline
\tabitem Dexterity \\
\tabitem Constitution \\
\tabitem Intelligence \\
		\end{tabularx}
\noindent Spell save DC $= 8 + 3 + 4 = 14$

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Weapons:}} \\
\hline
\tabitem Sabre (proficient) 1d8 slashing damage \\
\tabitem Pistol (proficient) 1d10 piercing damage \\
\tabitem Bombs (proficient) 3d6 fire damage \\
\tabitem Cutlass (proficient) 1d6 slashing damage \\
\tabitem Belaying Pin 1d4 bludgeoning damage \\
Hit $=$ 1d20 $+$ ab. mod. $+$ prof. \\
Damage $=$ W.D. $+$ ab. mod.
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Chosen Abilities and Traits:}} \\
\hline
\tabitem Pirate \\
\tabtabitem Bad Reputation \\
\tabitem Expertise \\
\tabtabitem Intimidation \\
\tabtabitem Medicine \\
\tabitem Sneak Attack \\
\tabtabitem 2d6 \\
\tabitem Thieves' Cant \\
\tabitem Cunning Action \\
\tabitem Magical Tinkering \\
\tabtabitem Shed Light \\
\tabtabitem Recorded Message \\
\tabtabitem Odour or Sound \\
\tabtabitem Visual Effect \\
\tabitem Infuse Item \\
\tabtabitem Enhanced Arcane Focus \\
\tabtabitem Enhanced Weapon \\
\tabtabitem Enhanced Defence \\
\tabtabitem Repeating Shot \\
\tabitem Experimental Elixir \\
\tabtabitem Healing, Swiftness, Resilience, \\
\tabtabitem Boldness, Flight, Transformation \\
\tabitem Mage Hand Legerdemain
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l c}
{\Large \textbf{Spell Slots:}} \\
\hline
1st level slot & \available \\
1st level slot & \available \\
1st level slot & \available \\
1st level slot & \available \\
2nd level slot & \available \\
2nd level slot & \available
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Item Proficiencies:}} \\
\hline
\tabitem Light Armour \\
\tabitem Medium Armour \\
\tabitem Shields \\
\tabitem Simple Weapons \\
\tabitem Pistols \\
\tabitem Sabres/Rapiers \\
\tabitem Scimitar/Cutlass \\
\tabitem Bombs \\
\tabitem Alchemist's Supplies \\
\tabitem Thieves' Tools \\
\tabitem Navigator's tools \\
\tabitem Vehicles (water) \\
\tabitem Brewer's supplies
		\end{tabularx}

\vspace{4mm}

\noindent \begin{tabularx}{\linewidth}{@{}l}
{\Large \textbf{Spell list}} 			\\
\hline
\textbf{Cantrips:}	 					\\
\tabitem Create Bonfire (A)			 	\\
\tabitem Guidance (A)					\\
\tabitem Mage Hand (R)					\\
\tabitem Minor Illusion (R)				\\
\tabitem Prestidigitation (R)			\\

\textbf{1st. Level Spells:}				\\
\tabitem Healing Words (A)				\\
\tabitem Ray of Sickness	(A)			\\
\tabitem Absorb Elements	(A) 		\\
\tabitem Catapult (A)					\\
\tabitem Faerie Fire (A)				\\
\tabitem Shield of Faith	(A)	 		\\
\tabitem Colour Spray (R)				\\
\tabitem Disguise Self (R)				\\
\tabitem Identify (R)					\\

\textbf{2nd. Level Spells:}				\\
\tabitem Levitate (A)
		\end{tabularx}
	\end{multicols}

\clearpage

	\begin{center}
{\LARGE \textbf{Items}}
	\end{center}

	\begin{tabularx}{\textwidth}{X|r}
Item & Weight [kg] \\
\hline
A belaying pin 								&  			\\
50 feet of silk rope						&  			\\
A foreign golden coin 						&  			\\
A set of common clothes 					&  			\\
A pouch		 								&  			\\
A Saber		 								&  			\\
A pistol	 								&  			\\
20 bullets	 								&  			\\
Backpack 									&  			\\
A Crowbar	 								&  			\\
A Hammer	 								&  			\\
10 pitons	 								&  			\\
10 torches	 								&  			\\
A tinderbox	 								&  			\\
10 days of rations							&  			\\
A waterskin 								&  			\\
50 feet of hemp rope 						&  			\\
2 daggers 									&  			\\
Studded Leather	 							&  			\\
Thieves' tools 								&  			\\
Cutlass		 								&  			\\
Alchemist's supplies 						&  			\\
5 bombs		 								&  			\\
20 gp					 					& 			\\
\hline
Sum 										& 
	\end{tabularx}

\vspace{10mm}

\textbf{Carrying capacity:} \\

	\begin{tabular}{l|c}
Category & Weight [kg] \\
\hline
Lightly encumbered 	& 0 - 30 	\\
Encumbered 			& 30 - 60 	\\
Heavily encumbered	& 60 - 90
	\end{tabular}
\end{document}