\documentclass[11pt, A4paper, english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage[colorlinks]{hyperref}
\usepackage{color}
\usepackage{tabularx}

\definecolor{url}{rgb}{0.1, 0.1, 0.4}

\hypersetup{colorlinks, urlcolor=url}

\author{Torstein Solheim Ølberg}
\title{Artificer Infusion Encyclopedia}


\begin{document}
\maketitle

\tableofcontents

	\section{2nd Level Infusions}
		\subsection{Enhanced Arcane Focus}
\textbf{Item:} A rod, staff or wand (requires attunement) \\
While holding this item, a creature gains a +1 bonus to spell attack rolls. In addition, the creature ignores half cover when making a spell attack. \\
The bonus increases to +2 when you reach 10th level in this class.

		\subsection{Enhanced Defence}
\textbf{Item:} A suit of armour or a shield \\
A creature gains a +1 bonus to Armour Class while wearing (armor) or wielding (shield) the infused item. \\
The bonus increases to +2 when you reach 10th level in this class.

		\subsection{Enhanced Weapon}
\textbf{Item:} A simple or martial weapon \\
This magic weapon grants a +1 bonus to attack and damage rolls made with it. \\
The bonus increases to +2 when you reach 10th level in this class.

		\subsection{Repeating Shot}
\textbf{Item:} A simple or martial weapon with the ammunition property (requires attunement) \\
This magic weapon grants a +1 bonus to attack and damage rolls made with it when it's used to make a ranged attack, and it ignores the loading property if it has it. \\
If you load no ammunition in the weapon, it produces its own, automatically creating one piece of magic ammunition when you make a ranged attack with it. The ammunition created by the weapon vanishes the instant after it hits or misses a target.

		\subsection{Replicate Magic Item}
\textbf{Item:} None \\
Using this infusion, you replicate a particular magic item. You can learn this infusion multiple times; each time you do so, choose a magic item that you can make with it, picking from the Replicable Items tables below. A table's title tells you the level you must be in the class to choose an item from the table. \\
In the tables, an item's entry tells you whether the item requires attunement. See the item's description in the Dungeon Master's Guide for more information about it, including the type of object required for its making. \\
If you have Xanathar's Guide to Everything, you can choose from among the common magic items in that book when you pick a magic item you can replicate with this infusion. \\
			\begin{tabularx}{107.5mm}{|l|l|c|}
\hline
Level Requirement	& Magic Item						& Attunement	\\
\hline
2nd level			& Alchemy Jug						& No			\\
2nd level			& Armblade							& Yes			\\
2nd level			& Bag of Holding					& No			\\
2nd level			& Cap of Water Breathing			& No			\\
2nd level			& Goggles of Night					& No			\\
2nd level			& Prosthetic Limb					& Yes			\\
2nd level			& Rope of Climbing					& No			\\
2nd level			& Sending Stones					& No			\\
2nd level			& Wand of Magic Detection			& No			\\
2nd level			& Wand of Secrets					& No 			\\
\hline
6th level			& Boots of Elvenkind				& No			\\
6th level			& Cloak of Elvenkind				& Yes			\\
6th level			& Cloak of Manta Ray				& No			\\
6th level			& Eyes of Charming					& Yes			\\
6th level			& Gloves of Thievery				& No			\\
6th level			& Lantern of Revealing				& No			\\
6th level			& Pipes of Haunting					& No			\\
6th level			& Ring of Water Walking				& No			\\
6th level			& Wand Sheath						& Yes			\\
\hline
			\end{tabularx} \\
			\begin{tabularx}{122.7mm}{|l|l|c|}
\hline
Level Requirement	& Magic Item						& Attunement	\\
\hline
10th level			& Boots of Striding and Springing	& Yes			\\
10th level			& Boots of the Winterlands			& Yes			\\
10th level			& Bracers of Archery				& Yes			\\
10th level			& Brooch of Shielding				& Yes			\\
10th level			& Cloak of Protection				& Yes			\\
10th level			& Eyes of the Eagle					& Yes			\\
10th level			& Gauntlets of Ogre Power			& Yes			\\
10th level			& Gloves of Missile Snaring			& Yes			\\
10th level			& Gloves of Swimming and Climbing	& Yes			\\
10th level			& Hat of Disguise					& Yes 			\\
10th level			& Headband of Intellect				& Yes			\\
10th level			& Helm of Telepathy					& Yes			\\
10th level			& Medallion of Thoughts				& Yes			\\
10th level			& Periapt of Wound Closure			& Yes			\\
10th level			& Pipes of the Sewers				& Yes			\\
10th level			& Quiver of Ehlonna					& No			\\
10th level			& Ring of Jumping					& Yes			\\
10th level			& Ring of Mind Shielding			& Yes			\\
10th level			& Slippers of Spider Climbing		& Yes			\\
10th level			& Ventilating Lungs					& Yes			\\
10th level			& Winged Boots						& Yes			\\
\hline
14th level			& Amulet of Health					& Yes			\\
14th level			& Arcane Propulsion Arm				& Yes			\\
14th level			& Belt of Hill Giant Strength		& Yes			\\
14th level			& Boots of Levitation				& Yes			\\
14th level			& Boots of Speed					& Yes			\\
14th level			& Bracers of Defence				& Yes			\\
14th level			& Cloak of the Bat					& Yes			\\
14th level			& Dimensional Shackles				& No			\\
14th level			& Gem of Seeing						& Yes			\\
14th level			& Horn of Blasting					& No			\\
14th level			& Ring of Free Action				& Yes			\\
14th level			& Ring of Protection				& Yes			\\
14th level			& Ring of the Ram					& Yes			\\
\hline
			\end{tabularx}

		\subsection{Returning Weapon}
\textbf{Item:} A simple or martial weapon with the thrown property \\
This magic weapon grants a +1 bonus to attack and damage rolls made with it, and it returns to the wielder's hand immediately after it is used to make a ranged attack.



	\section{6th Level Infusions}
		\subsection{Boots of Winding Path}
\textbf{Item:} A pair of boots (requires attunement) \\
While wearing these boots, a creature can teleport up to 15 feet as a bonus action to an unoccupied space the creature can see. The creature must have occupied that space at some point during the current turn.

		\subsection{Homunculus Servant}
\textbf{Item:} A gem worth at least 100 gp or a dragonshard \\
You learn intricate methods for magically creating a special homunculus that serves you. The item you infuse serves as the creature's heart, around which the creature's body instantly forms. \\
You determine the homunculus's appearance. Some artificers prefer mechanical-looking birds, whereas some like winged vials or miniature, animate cauldrons. \\
The homunculus is friendly to you and your companions, and it obeys your commands. See this creature's game statistics in the Homunculus Servant stat block. \\
In combat, the homunculus shares your initiative count, but it takes its turn immediately after yours. It can move and use its reaction on its own, but the only action it takes on its turn is the Dodge action, unless you take a bonus action on your turn to command it to take the action in its stat block or the Dash, Disengage, Help, Hide, or Search action. \\
The homunculus regains 2d6 hit points if the mending spell is cast on it. If it dies, it vanishes, leaving its heart in its space. \\
			\begin{tabularx}{125.7mm}{|l|}
\hline
{\large \textbf{Humonculus Servant}} \\
Tiny construct, neutral \\
\hline
Armour Class: 13 (natural armour) \\
Hit Points $=$ its Con. mod. $+$ your Int. mod. $+$ your Art. lvl. \\
Speed: 20 (30 flying) \\
Strength: 4 (-3) \\
Dexterity: 15 (+2) \\
Constitution: 12 (+1) \\
Intelligence: 10 (0) \\
Wisdom: 10 (0) \\
Charisma: 7 (-2) \\
Saving Throw Bonus: Dex (+4) \\
Skill Bonuses: Perception (+4), Stealth (+4) \\
Damage Immunity: Poison \\
Condition Immunity: Exhaustion, Poisoned \\
Darkvision: 60 feet \\
Passive Perception: 14 \\
Languages: Same as manufacturer \\
\textbf{Evasion:} \\
If the homunculus is subjected to an effect that allows it to make a \\
Dexterity saving throw to take only half damage, it instead takes no \\
damage if it succeeds on the saving throw, and only half damage if it \\
fails. It can't use this trait if it’s incapacitated. \\
\textbf{Might of the Master:} \\
The following numbers increase by 1 when your proficiency bonus \\
increases by 1: the homunculus's skill and saving throw bonuses (above) \\
and the bonuses to hit and damage of its attack (below). \\
\textbf{Force Strike:} \\
Cost: 1 bonus action from you. Ranged Weapon Attack: +4 to hit, \\
range 30 feet, one target you can see. Damage: 1d4 + 2 force damage. \\
\textbf{Channel Magic:} \\
Cost: reaction. The homunculus delivers a spell you cast that has a \\
range of touch. The homunculus must be within 120 feet of you. \\
\hline
			\end{tabularx}

		\subsection{Radiant Weapon}
\textbf{Item:} A simple or martial weapon (requires attunement) \\
This magic weapon grants a +1 bonus to attack and damage rolls made with it. While holding it, the wielder can take a bonus action to cause it to shed bright light in a 30-foot radius and dim light for an additional 30 feet. The wielder can extinguish the light as a bonus action. \\
The weapon has 4 charges. As a reaction immediately after being hit by an attack, the wielder can expend 1 charge and cause the attacker to be blinded until the end of the attacker's next turn, unless the attacker succeeds on a Constitution saving throw against your spell save DC. The weapon regains 1d4 expended charges daily at dawn.

		\subsection{Repulsion Shield}
\textbf{Item:} A shield (requires attunement) \\
A creature gains a +1 bonus to Armour Class while wielding this shield. \\
The shield has 4 charges. While holding it, the wielder can use a reaction immediately after being hit by a melee attack to expend 1 of the shield's charges and push the attacker up to 15 feet away. The shield regains 1d4 expended charges daily at dawn.

		\subsection{Resistant Armour}
\textbf{Item:} A suit of armour (requires attunement) \\
While wearing this armour, a creature has resistance to one of the following damage types, which you choose when you infuse the item: acid, cold, fire, force, lightning, necrotic, poison, psychic, radiant, or thunder.

\end{document}